Understanding the Lomb-Scargle Periodogram

### 2017-01-31 PracticalLombScargle.tex
Add CLEAN discussion & some missing references

The left panel of \fig{LINEAR-power} shows the Lomb-Scargle periodogram computed for the data in \fig{LINEAR-data}.
Computing the Lomb-Scargle periodogram for the data gives us a measure of the
power as a function of period of oscillation (\fig{LINEAR-power}, left), from
which we can determine the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.\footnote{
    The periodogram in \fig{LINEAR-power} was computed using
    {\tt astropy.stats.LombScargle}
    from the AstroPy project; see \url{http://astropy.org/}.
}

@@

\todo{Add simulated RR Lyrae data and show the Shuster periodogram}

@@

@@

While the False Alarm Probability can be a useful concept, you should be
careful to keep in mind that it answers a very specific question:
{\it what is the probability that a signal with no periodic component would
lead to a peak of this magnitude?}
In other words, it is a measure of the false positive rate: the rate at which
we would expect to incorrectly identify a periodic signal where none
actually exists.
It tells us nothing about the false negative rate; {i.e.} the rate at which
we would expect to miss a periodic signal that is, in fact, present.
It also tells us nothing about the error rate; {i.e.} the rate at which we
would expect to identify an incorrect alias of a signal present in our data
(as we saw in \sect{failure-modes}).
Too often users are tempted to interpret the FAP too broadly, with the hope that
it would speak to these questions as well.

To the best of my knowledge, there is currently no silver bullet for answering
these broader questions within the Lomb-Scargle approach.
Perhaps the most fruitful path toward understanding of such effects for a
particular survey---with particular noise characteristics and a particular
observing window---is via simulated data.
In fact, this type of simulation is a vital component of most current and
future time-domain surveys that seek to catalog periodic objects
\citep[see, e.g.][]{opsim1, opsim2, Ivezic08LSST}
\todo{refs for SDSSII, Kepler, PanSTARRS, Gaia}.

>>>>

The left panel of \fig{LINEAR-power} and its inset show the Lomb-Scargle periodogram computed for the data in \fig{LINEAR-data}.
Computing the Lomb-Scargle periodogram for the data gives us a measure of the
power as a function of period of oscillation (\fig{LINEAR-power}, left), from
which we can determine the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.\footnote{
    The periodogram in \fig{LINEAR-power} was computed using
    {\tt astropy.stats.LombScargle}
    from the AstroPy project; see \url{http://astropy.org/}.
}

@@

@@

\subsection{A Note on Window Deconvolution}

There have been a few attempts in the literature to use procedural algorithms
to solve this under-constrained deconvolution problem, perhaps most notably
by adapting the iterative CLEAN algorithm developed for deconvolution in the
context of radio astronomy \citep{Roberts87}.
For cleaning of Lomb-Scargle periodograms, the CLEAN approach is hindered by
three main deficiencies: first and most importantly, the CLEAN algorithm at each
iteration assumes that the highest peak is the location of the primary signal;
this is not always borne out for realistic observations of faint objects where
the cleaning is most necessary (see the discussion in \sect{failure-modes}).
Second, the convolution takes place at the level of the Fourier transform
rather than the PSD; trying to clean a PSD directly ignores important phase
information. Third, the CLEAN algorithm assumes a Schuster-type FFT analysis:
while the Lomb-Scargle periodogram is equivalent to Schuster in the limit of
equally-spaced observations, it is not equivalent in the relevant case of
unequal observations (see \sect{schuster-to-lomb-scargle}),
and so any attempt to apply CLEAN to Lomb-Scargle
analysis directly is fundamentally flawed.

My feeling is that there is room for a more principled approach to the
unconstrained deconvolution problem for periodograms derived from non-uniform
fast Fourier transforms (perhaps through some sort of regularization),
but this does not appear to have been explored anywhere in the astronomy
literature.

@@

While the False Alarm Probability can be a useful concept, you should be
careful to keep in mind that it answers a very specific question:
{\it what is the probability that a signal with no periodic component would
lead to a peak of this magnitude?}
In other words, it is a measure of the false positive rate: the rate at which
we would expect to incorrectly identify a periodic signal where none
actually exists.
It tells us nothing about the false negative rate; {i.e.} the rate at which
we would expect to miss a periodic signal that is, in fact, present.
It also tells us nothing about the error rate; {i.e.} the rate at which we
would expect to identify an incorrect alias of a signal present in our data
(as we saw in \sect{failure-modes}).
Too often users are tempted to interpret the FAP too broadly, with the hope that
it would speak to these additional questions as well.

To the best of my knowledge, there is currently no silver bullet for answering
these broader questions within the Lomb-Scargle approach.
Perhaps the most fruitful path toward understanding of such effects for a
particular survey---with particular noise characteristics and a particular
observing window---is via simulated data injected into the detection
pipeline.
In fact, this type of simulation is a vital component of most (if not all)
current and future time-domain surveys that seek to catalog periodic objects,
regardless of the particular approach used to detect periodicity
\citep[see, e.g.][]{opsim1, opsim2, Ivezic08LSST, Sesar2010, Oluseyi12, McQuillan2012, Drake2014}
